Extreme Value Chapter 3

### 2022-03-02 Ch3_samplesize/Figures_Ch3.Rmd
Writing code to see if it works to bring in the other mixture simulations.

@@

>>>>

bias_bxplot_fx <- function(data){
  data %>% 
  dplyr::select(., thresh_tests, samp_n_tests, gp_theta_hat, gp_theta_bar, theta) %>%
  mutate(original = log(gp_theta_hat/theta),
         corrected = log(gp_theta_bar/theta)) %>%
  pivot_longer(., cols = c(original, corrected), names_to = "type", values_to = "theta_val") %>%
  drop_na() %>%
  mutate(thresh_tests = factor(thresh_tests),
         samp_n_tests = factor(samp_n_tests)) %>% 
  mutate(labelsamp = paste("n =", samp_n_tests),
         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
  ggplot(., aes(x = thresh_tests, y = theta_val, color = type, fill = type)) +
  facet_wrap(~labelsamp, nrow = 1) +
  geom_boxplot() +
  scale_color_manual(values = dens_cols[c(1,4)], name = "Bias") +
  scale_fill_manual(values = dens_cols[c(2,3)], name = "Bias") +
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  labs(y = TeX(r'($log(\hat{\theta} / \theta)$)'), x = "Distance Level Estimated") +
  theme_bw()
}

@@

dir_scenario <- "ain1_samesd_upmean"
load(paste0("Ch3_samplesize/", dir_scenario, "/allin1df.RData"))

B1 <- bias_bxplot_fx(allin1df)
